{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-22 documents/application.tex
writing!

SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.

@@

\footnotetext{In our case, it seems to make the most sense to discuss the attenuation of the electric field, V/m, rather than the field power (also referred to as the {\it intensity}),\Wsqm, since the inactivation seems most closely related to the former. Strictly speaking, penetration depth refers to the depth at which the power is reduced by 1/$e$; skin depth, where the electric field is 1/$e$. The penetration depth is simply half the skin depth.\cite{Penetration2019a} If we refer to penetration depth without making this explicit, we are referring to the electric field penetration depth.}

Conduction effects. Because the transmission line voltage only goes as the to the square root of the input power

@@

It is difficult to intuit how 40,000 watts can possibly be safe. It's useful to note, however, that the total energy dissipated in each pulse is . An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; while no clinical data are available, whispering at someone is rarely considered calamitous\citationneeded!

>>>>

SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013].

@@

\footnotetext{In our case, it seems to make the most sense to discuss the attenuation of the electric field, V/m, rather than the field power (also referred to as the {\it intensity}),\Wsqm, since the inactivation seems most closely related to the former. Strictly speaking, penetration depth refers to the depth at which the power is reduced by 1/$e$; skin depth, where the electric field is 1/$e$. The penetration depth is simply half the skin depth.\cite{Penetration2019a} If we refer to penetration depth without making this distinction explicit, we are referring to the electric field penetration depth.}

Conduction effects. Because the transmission line voltage only goes as the square root of the input power

@@

It is difficult to intuit how 40,000 watts can possibly be safe. It's useful to note, however, that the total energy dissipated in each pulse is . An oft-cited figure for the energy in a whisper is 10 mJ; while no clinical data are available, whispering at someone is rarely considered calamitous\citationneeded!

### 2020-11-22 documents/background.tex
writing!

Previous works (Liu et al, ) appear to demonstrate that several species of viruses exhibit an anomalous dielectric relaxation time of $> 75 \text{ ps}$, as opposed to $< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\

@@

is is apparently easy to draw the wrong conculsion from a funnel plot, however. Here's one example of a flawed analysis: http://ies.fsv.cuni.cz/sci/publication/show/id/5277/lang/cs

Thanks to James Picone https://skeptics.stackexchange.com/a/49751/ for the analysis.

"The funnels are heavily asymmetrical: the left-hand side of the funnels is almost completely missing, hence we have good reason to believe that publication selection bias is strong in this literature." -

\subsection{Artifacts in past absorption spectroscopy experiments}

@@

Such an effect is so unexpected - Bigio et  aldescribe it as “astonishing”. Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect. This result seems to have triggered a large amount of work to model this interaction, and various other interactions, in an attempt to explain the observed resonance.

@@

Unfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.

@@

@@

>>>>

One of the assumptions that underpin

Previous works (Liu et al, ) appear to demonstrate that several species of viruses exhibit an anomalous dielectric relaxation time of $> 75 \text{ ps}$, as opposed to $<< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\

@@

\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development of non-classical damping hypotheses}

@@

Such an effect is so unexpected - Bigio et al describe it as “astonishing”. Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect. This result seems to have triggered a large amount of work to model this interaction, and various other interactions, in an attempt to explain the observed resonance.

@@

\lettrine{U}nfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.

@@

\subsection{Meta issues with the field}

\footnotetext{
It is apparently easy to draw the wrong conculsion from a funnel plot, however. Here's one example of a flawed analysis: http://ies.fsv.cuni.cz/sci/publication/show/id/5277/lang/cs

Thanks to James Picone https://skeptics.stackexchange.com/a/49751/ for the analysis.
}

@@

anthropic principle

\subsection{Raman spectroscopy}

Very recently, Burkhartsmeyer \cite{Optical2020} have published data replicating the findings using a single-particle Raman spectroscopy technique. We have not examined these claims in detail, but they are good evidence.

Non-photothermal optical Raman methods can also apparently synthesize artifacts - see unpublished, personal communication with Taylor \cite{mechanisms1981}.

### 2020-11-22 documents/detection.tex
writing!

%!TeX root = background
\documentclass[paper.tex]{subfiles}
\begin{document}

@@

- Detect the growth of the host bacteria, and measure effects of the phage on that growth

- Plaque plating

@@

Plates are super sensitive, but in general I didn’t have huge issues with contamination; even my bad aseptic technique was fine - perhaps 1 contaminant region per plate.

- Detect the lysis of bacteria, the release of intracellular material

@@

Detect the lysis of the virus, and the release of intra-viral material

@@

Directly detect the virus itself

PEG apparently concentrates to 10^12 or 13 no matter what the starting concentration is (huh?), very convenient.

>>>>

%!TeX root = detection
\documentclass[paper.tex]{subfiles}
\begin{document}

\begin{autem}
	I hasten to note that quantifying phage titer is a completely solved problem, and is a procedure often done in kindergarten labs. The amount of time and effort we spent here was completely unjustifiable. It was driven by an acute lack of competence, equipment, and the small volume constraints of our original poorly designed microwave setup.
\end{autem}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{chunk_4}
	\caption{
		\light{
			\\
			We've got a thing\\
			that's called\\
			{\it Radar Love}\\}
		We've got a wave\\
		in the air}
\end{figure}

Essentially the only method of determining the activity of phage is to have it infect a suitable host.

Typically, this is done either in a large tube or a flat-sided optical cuvette.

Because the variation in the optical density is quite small, this poses some rather.

A lot of the basic facts of phage were determined in the 1930s;

A small vial of liquid has a much larger surface area relative to its thermal mass. sis removed, the temperature drops very rapidly; if the temperature drops outside the "physiological range" of around 33-40 C, growth is stunted \cite{effect2003}. \cite{growth1946}. I'm not sure if this was the problem I encountered,

As a faculative aerobe, E.coli requires a concentration of oxygen to be present in the mixture for speedy replication \cite{Effect1965}; and this supply must also be kept sterile. One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters.

Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; the Manganese dioxide catalyzed decomposition of hydrogen peroxide. $MnO_2$ is readily obtained from alkaline batteries; and in this case no sterility issues are presented. However, it is not obvious how antimicrobial $H_2O_2$ vapor can be prevented from contacting the culture.

Bottles of zero air may be more effective.

In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to an enclosing cabinet.

Shaking incubators, where the flasks are

Ensuring that a great deal of headspace was present in a sealed tube (that is, culturing 2.5 mL in a 15 mL falcon tube) was sufficient for brief, low-density.

As the size of the well decreases, the Reynolds number also decreases \footnote{In fact, in the case of a circular well, it's not obvious that this is the case - the cross section decreases faster than the characteristic length}, and turbulent flow is greatly hampered.

Even slight rotation of the tube, such that the graduations

"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue; tetrazolium dye methods;

Using 2.5 mm diameter x 3 mm high wells cut in polycarbonate and sealed with clear packing tape. However, the presence of small bubbles in the headspace of the wells prevented a consistent reading.

We tried simply adding 1 uL of culture to the microscope slide;

The 8-bit resolution and dynamic range of most cameras did not seem sufficient to discern the turbidity; and masking and correcting for

\cite{Vision2016} use an ingenious technique. A background with sharp light-to-dark edges is used. Slicing the image into chunks only slightly larger than the object,

The 0.8 uL sample in each was not sufficient to produce a measurable change in turbidity in a 0.2 uL - or we were not experienced enough to perform the phage lysis protocol properly.

However, we were not able to make smaller volumes of culture enter the log phase.

Another very interesting technique is that of \cite{Study2003},

@@

\subsection{Detect the growth of the host, and measure effects of the virus on that growth}

\subsubsection{Plaque assay}

The plaque assay for viruses has remained essentially unchanged since Delbruck's era.

Advantages over broth methods are the longer infective period without agitation or

@@

Despite poor aseptic technique, contamination was not a serious issue - perhaps 1 contaminant region per plate.

Incubating the bacterial lawn for sufficient contrast to read the plaques imposes a ~1 to 3 day delay between test and results. Each test requires several dilution tubes

\subsubsection{Broth assays}

This, however, requires a microplate reader which can simultaneously agitate for sufficient oxygen, incubate, and

Tetrazolium dyes are metabolized

GFP

\subsubsection{Detect the release of intracellular material due to the lysis of the host}

One common target is the enzyme $\beta$-galactosidase. E. coli and other. Both  isopropyl $\beta$-D-thiogalactoside. Lactose itself is a reasonable substitute (Borralho \cite{Lactose2002}).

Ijzerman

X-gal \cite{Improved}

I was introduced to this by Ijzerman \cite{liquid1993}, who recommend chlorophenol red $\beta$-D-galactopyranoside (CPRG) as the chromogen for a high sensitivity. CPRG is very hard to obtain except through Sigma.

@@

\includegraphics[width=\textwidth]{x_gal.jpg}

\includegraphics[width=\textwidth]{x_gal_and_flourescence/CIMG6810.JPG}

@@

\subsubsection{Detect the lysis of the virus, and the release of intra-viral material}

\subsubsection{Directly detect the virus itself}

Phages release several small compounds like putrescine and spermadine when broken (Minagawa\cite{characteristics1961}). These can be indicated colorimetrically at ppm scales with ninhydrin, or at nanogram scales via fluorescamine.

Otherwise, GFP-flouresecent strains of E. coli, or phage which has been labelled with a

PEG apparently concentrates to $10^{12}$ or 13 no matter what the starting concentration is (huh?), very convenient.

### 2020-11-22 documents/pseudo_soliton.tex
writing!

Precursor waves do not appear to be explicitly mentioned in C95- but are implicitly governed by the Fourier-spectrum clauses. Ultra-short wavepackets of a similar nature are widely used in MRI systems with a repetition rate up to 300 MHz. We can make some mechanistic claims.

At 9 GHz, assuming that a torso is about 10 penetration depths in radius, implementing this would decrease the required surface field for complete eradication of the virus from the body to only 1 kV/m, rather than 6.6 MV/m ($1/\sqrt{10}=0.316$ rather than $e^{-10}=4.5e-5$).

There are some extremely tricky subtleties in the simulation.  \cite{propagation1992}. In \cite{Comments1993}, Leubbers says FDTD and FFT both are better than Asympt, Ogh says no there's no problem, Asymptotic is really accurate. Frankly, I can't make heads or tails of any of these, not understanding the asymptotic method at all.

>>>>

Uzunoglu \cite{Theoretical2020} cite a very handy way to circumvent this lossy-flesh problem: the Brilloin and Somerfield precursors.

At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the brilluoin train drives the virus with an equally, implementing this would decrease the surface field required for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e-5$).

Precursor waves do not appear to be explicitly mentioned in IEEE standards, but are implicitly governed by the Fourier-spectrum clauses and more recent FCC ultrawideband regulations. Ultra-short wavepackets of a similar nature are widely used in MRI systems with a repetition rate up to 300 MHz. We can make some mechanistic claims.

\footnotetext{
	Sincere thanks go to the legendary Kurt Oughstun for taking the time to thoroughly answer some of our questions.
}

\begin{sidenote}
There are some extremely tricky subtleties in the simulation.  \cite{propagation1992}. In \cite{Comments1993}, Leubbers says FDTD and FFT both are better than Asympt, Ogh says no there's no problem, Asymptotic is really accurate. Frankly, I can't make heads or tails of any of these, not understanding the asymptotic method at all.
\end{sidenote}
